Ornaments as indicators of social changes and cultural practices in northeastern Taiwan before and after European colonial period

### 2019-12-11 analysis/paper/paper.Rmd
edit the data file, work on the code for table, get an error

kw_dates_with_error_calibrated <- 
  with(kw_dates_with_error,
       BchronCalibrate(
         ages = rce,
         ageSds = se,
         ids = id,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce))
       ))

@@

```{r C14-table-data}
table_kw_dates <-
  kw_dates %>% 
  mutate(`Above mean sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>% 
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  left_join(kw_age_cali_df_tidy, "Pit-Layer") %>% 
  mutate(ave = (`2.5%` + `97.5%`) / 2) %>% 
  mutate(ave = ifelse(is.na(ave), 200, ave)) %>%  
  arrange(ave) %>% 
  dplyr::select("Pit-Layer", "Above mean sea level (cm)", "Date BP", "Calibrated date (95% conf. level)", "Details") %>% 
  mutate(`Calibrated date (95% conf. level)` = 
           ifelse(is.na(`Calibrated date (95% conf. level)`), "—", `Calibrated date (95% conf. level)`))

>>>>

kw_dates_with_error_calibrated <- 
  with(kw_dates_with_error,
       BchronCalibrate(
         ages = rce,
         ageSds = se,
         ids = id,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce))))

@@

```{r C14-table-data}
table_kw_dates <-
  kw_dates %>% 
  mutate(`Above mean sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>% 
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  left_join(kw_age_cali_df_tidy, "Pit-Layer") %>% 
  mutate(ave = (`2.5%` + `97.5%`) / 2) %>% 
  mutate(ave = ifelse(is.na(ave), 200, ave)) %>%  
  arrange(ave) %>% 
  dplyr::select("Lab code", "Pit-Layer", "Above mean sea level (cm)", "Date BP", "Calibrated date (95% conf. level)", "Details") %>% 
  mutate(`Calibrated date (95% conf. level)` = 
           ifelse(is.na(`Calibrated date (95% conf. level)`), "—", `Calibrated date (95% conf. level)`))
